Title Goes Here

### 2021-04-13 analysis/paper/shceof.Rmd
Quita figura de ZW1 de O3 vs cEOF1
#34

```{r wave1-o3, fig.cap = "(ref:wave1-o3-cap)", fig.width=width_column, fig.height=width_column*.7}
wave1_o3 <- o3 %>% 
  .[lat %between% o3wave_lats] %>% 
  .[, .(toc = mean(toc, na.rm = TRUE)), by = .(time, lon)] %>% 
  .[, FitWave(toc, 1), by = .(time)]

@@

# temp %>% 
#   copy() %>% 
#   na.omit() %>% 
#   sep_ReIm() %>% 
#   .[, hgt := scale(hgt), by  = .(part)] %>% 
#   ggplot(aes(amplitude, hgt)) +
#   geom_point() +
#   geom_smooth(method = "lm", color = "black") +
#   facet_grid(cEOF ~ part) +
#   panel_background
# temp %>% 
#   .[, correlate(amplitude, Mod(hgt))]
# 
# temp %>% 
#   .[, correlate(phase, Arg(hgt))]

@@

Indeed, Figure\ \@ref(fig:wave1-o3) shows the relationship between amplitude and phase of the cEOF1 and the amplitude and phase of the planetary wave 1 in Total Ozone Column between `r knitr::combine_words(LatLabel(o3wave_lats))`; as shown in Figure\ \@ref(fig:o3-regr), this is a wide latitude band that captures most of the area with significant regression coefficients. The correlation between the zonal wave 1 of ozone and cEOF1 (computed as the mean cosine of the difference in phase) is `r wave_correlation$text`. As expected from the location of anomalies in Figure\ \@ref(fig:wave1-o3), the Real cEOF1 drives the relationship with amplitude and the Imaginary cEOF1 drives the relationship with phase (not shown).

>>>>

```{r wave1-o3, fig.cap = "(ref:wave1-o3-cap)", fig.width=width_column, fig.height=width_column*.7, include = FALSE}
wave1_o3 <- o3 %>% 
  .[lat %between% o3wave_lats] %>% 
  .[, .(toc = mean(toc, na.rm = TRUE)), by = .(time, lon)] %>% 
  .[, FitWave(toc, 1), by = .(time)]

@@

# temp %>% 
#   copy() %>% 
#   na.omit() %>% 
#   sep_ReIm() %>% 
#   .[, hgt := scale(hgt), by  = .(part)] %>% 
#   ggplot(aes(amplitude, hgt)) +
#   geom_point() +
#   geom_smooth(method = "lm", color = "black") +
#   facet_grid(cEOF ~ part) +
#   panel_background
wave1_cor <- rbind(temp %>%
                     .[, correlate(amplitude, Mod(hgt))] %>% 
                     .[, with := "amplitude"],

                   temp %>%
                     .[, correlate(phase, Arg(hgt))] %>% 
                     .[, with := "phase"])

@@

There is a close relationship between amplitude and phase of the cEOF1 and the amplitude and phase of the planetary wave 1 in Total Ozone Column between `r knitr::combine_words(LatLabel(o3wave_lats))`; as shown in Figure\ \@ref(fig:o3-regr), this is a wide latitude band that captures most of the area with significant regression coefficients. The correlation between the amplitude of each index is `r wave1_cor[with == "amplitude"]$text` the overall correlation between the zonal wave 1 of ozone and cEOF1 (computed as the mean cosine of the difference in phase) is `r wave_correlation$text`. As expected from the location of anomalies in Figure\ \@ref(fig:o3-regr), the Real cEOF1 drives the relationship with amplitude and the Imaginary cEOF1 drives the relationship with phase (not shown).
